\chapter*{\centering{\emph{\large{ABSTRACT}}}}
\singlespacing{}

\textbf{PRAMUDIO}, Detection of around Wound Perimeter Using the 
Border Following Algorithm with the Help of Spline Interpolation. Undergraduate Thesis, Computer Science Program, Faculty of 
Mathematics and Natural Sciences, State University of Jakarta. July 2024.
\\
\\
Chronic wounds one of complex illness, particularly for whose suffer 
Diabetes Mellitus (DM). The process of wound healing need to be monitored 
by medical worker with assessment, which measure area of wound and looking at 
the color of the wound. After the assessment, medical worker will make a decision 
for the wound treatment. 
The wound healing process involves appropriate assessment 
and effective management, yet manual methods in wound measurement often 
time-consuming and potentially interfere with healing. This thesis aims to 
help the medical worker to chronic wound assessment using the method of 
border following with the help of spline interpolation in image processing 
to lessen manual chronic wound assessment. This research holds the potential 
to bring analysis that are objective and reliable on the uses of image 
processing for chronic wound assessment. By utilizing technology of 
image processing, researcher tried to overcome the limitations of manual 
methods of chronic wound assessment with border following algorithm. 
The first to do with this method is to use phone to capture a photo, 
followed by croping the photo to increase accuracy, then border following 
method run on photo that are cropped to get curve area around the wound, 
next smoothed by using spline interpolation. This method used on three kind 
of wound; red, yellow and black with the quantity of 69 image data. This experiment 
bring forth border following can only detect 14 wound with the average of accuracy; 
red 70.9$\%$ with 4 wounds, yellow 73.4$\%$ from 2 wounds, and black 92.6$\%$ 
on 8 wounds.
\\
\\
\textbf{Keywords}: chronic wounds, border following, spline interpolation, 
image processing, wound assessment, wound healing.
